\title{Fooling Sets}
\author{Jake Kinsella}
\date{\today}

\documentclass[12pt]{article}

\input{../tiling/header}

\begin{document}
\maketitle

Consider a two-party protocol for determining whether two inputs are equal:
\begin{equation}
  EQ(x, y) =
  \begin{cases}
    1 \text{ if x=y} \\
    0 \text{ otherwise}
  \end{cases}
\end{equation}


The "obvious protocol" is for Player 1 to send it's entire input to Player 2 and let Player 2 compare the values itself.
\\

\textbf{Protocol $\Pi$}
\begin{center}
  \begin{tabular}{ |m{15em}|m{15em}| } 
    \hline
    Player 1                   & Player 2 \\ [0.5ex] 
    \hline
    $x=111$                    & $y=110$ \\
    $P_{1}(x) \longrightarrow$ &  \\
                               & $p_{1} = 111$ \\
                               & $\longleftarrow P_{2}(y, p_{1}) = P_{2}(110, 111) = 0$ \\
    $p_{2} = 0$                & \\
    \hline
  \end{tabular}
\end{center}

In this example, 4 bits are communicated. More generally the $C(\Pi) = |x| + 1$, the cost for Player 1 to communicate x
plus one bit for Player 2 to communicate the answer.
\\

\textbf{Theorem:} $C(EQ) \geq n$
\\

\textbf{Claim:} For any $(x, x)$ and $(x', x')$, if on both inputs, both Players communicate the exact same sequence of
bits, then $f(x, x) = f(x', x') = f(x, x') = f(x', x)$

\begin{multicols}{2}

  $(x, x)$
  \begin{center}
    \begin{tabular}{ |m{7em}|m{7em}| } 
      \hline
      Player 1                   & Player 2 \\ [0.5ex] 
      \hline
      $x$                        & $x$ \\
      $P_{1}(x) \longrightarrow$ &  \\
                                 & $p_{1}$ \\
                                 & $\longleftarrow P_{2}(x, p_{1})$ \\
      $p_{2}$                    & \\
      \hline
    \end{tabular}
  \end{center}

\columnbreak

  $(x', x')$
  \begin{center}
    \begin{tabular}{ |m{7em}|m{7em}| } 
      \hline
      Player 1                   & Player 2 \\ [0.5ex] 
      \hline
      $x$                        & $x$ \\
      $P_{1}(x') \longrightarrow$ &  \\
                                 & $p_{1}'$ \\
                                 & $\longleftarrow P_{2}(x', p_{1}')$ \\
      $p_{2}'$                   & \\
      \hline
    \end{tabular}
  \end{center}

\end{multicols}

$p_{1} = p_{1}'$ and $p_{2} = p_{2}'$
$p_{2} = p_{2}'$ is the final answer.
\\

If $(x, x)$ and $(x', x')$ have the same communication pattern, then it doesn't matter which way the inputs are mixed.
Each $x$ and $x'$ produce the same bits.
\\

If they produce the same sequence of bits, then they agree on the output (as the output is just the final bit).
\\

\textbf{Proof:} $C(EQ) \geq n$
\\

Assume a protocol $\Pi'$ with complexity $n - 1$ exists that solves $EQ$.
\\

$\Pi'$ has $2^{n - 1}$ (${0, 1}$ over $n - 1$ bits) possible communication patterns if it can communicate a max $n - 1$
bits.
\\

However, there are $2^{n}$ input pairs $(x, x)$ ($|x| = n$, ${0, 1}$ over $n$ bits)
\\

$\Pi'$ has $2^{n - 1}$ possible communication patterns.
However there are $2^{n}$ equal input pairs.

Thus there exists some:
$(x, x)$ and $(x', x')$ where $x \neq x'$ that have the same communication protocol
\\

This is a contradiction.
\\
$EQ(x, x') = 0 \neq EQ(x, x)$
\\

Thus: $C(EQ) \geq n$
\\

\textbf{Lemma (generalization of the above theorem)}: Given some $f : {0, 1}^{n} \times {0, 1}^{n} \rightarrow {0, 1}$. $f$
has a M-sized fooling set if there exists an M-sized subset $S \subset {0, 1}^{n} \times {0, 1}^{n}$ and a value
$b \in {0, 1}$ such that:
\par{1) $\forall (x, y) \in S, f(x, y) = b$}
\par{2) $\forall distinct (x, y), (x', y') \in S, either f(x, y') \neq b or f(x', y) \neq b$}
\\
If $f$ has a size-M fooling set, then $C(f) \geq log(M)$
\\

\textbf{Example:}
\par{Determining whether two sets are disjoint across two parties.}

\par{$x, y \subset {1, 2, ..., n} \\$}
\\
\par{
  \begin{equation}
    DISJ(x, y) =
    \begin{cases}
      1 \text{ if } x \cap y = \emptyset \\
      0 \text{ otherwise}
    \end{cases}
  \end{equation}
}

\par{Fooling set for $DISJ$:}

\par{$S = {(A, \overline{A}) | A \subset {1, 2, ..., n}}$}
\par{\hspace{\parindent} 1) $\forall A, DISJ(A, \overline{A}) = 1$}
\par{\hspace{\parindent} 2) $\forall (A, \overline{A}), (B, \overline{B}), either DISJ(A, \overline{B}) = 0 or DISJ(B, \overline{A}) = 0$}
\\
\par{There are $2^{n}$ possible A sets}
\\
\par{Thus S is a $2^{n}$-sized fooling set}
\\
\par{Therefore $C(DISJ) \geq log(M) \geq n$}

\end{document}