\title{The 2-Party Discrepency Method}
\author{Max von Hippel}
\date{\today}

\documentclass[12pt]{article}

\include{header}

\begin{document}
\maketitle

\section{Introduction}

When we partition $M(f)$ into some number of rectangles,
	the sizes of the rectangles must add up to the size of $M(f)$.
Hence, if $\chi(f) \leq K$ for some integer $K$,
	then $M(f)$ must have a monochromatic rectangle containing at least $2^n * 2^n / K$ entries.
\begin{proof}
Suppose that $\chi(f) \leq K$ for some integer $K$.
If $\chi(f) = K$ then there exists a partioning of $M(f)$ into $K$ monochromatic rectangles, in which case at least one of those rectangles must have size $\geq \abs{M(f)} / K$, i.e., $2^n * 2^n / K$.  On the other hand if $\chi(f) < K$ then $\chi(f) = K'$ for some $K' < K$ and then $M(f)$ can be partitioned into $K'$ monochromatic rectangles, at least of which has size $\geq \abs{M(f)} / K'$, which is strictly larger than $\abs{M(f)} / K$.  So in either case the result holds and we are done.
\end{proof}
Now, suppose that $M(f)$ contains a monochromatic rectangle $A \times B$ having at least $2^n * 2^n / K$ entries.
Since $A \times B$ is monochromatic, this implies that:
\[\sum_{a \in A, b \in B} (-1)^{M_{a,b}} = \begin{cases}
-1 * \text{ the size of the rectangle } A \times B & \text{ if it's colored } 1 \\
 1 * \text{ the size of the rectangle } A \times B & \text{ if it's colored } 0\end{cases}\]
So if we wrap an absolute value above our sum, we get:
\[\abs{\sum_{a \in A, b \in B} (-1)^{M_{a,b}}} = \text{ the size of the rectangle } A \times B\]
But we already assumed that $A \times B$ has at least $2^n * 2^n / K$ entries, hence:
\[\abs{\sum_{a \in A, b \in B} (-1)^{M_{a,b}}} = \text{ the size of the rectangle } A \times B \geq 2^n * 2^n / K\]
Let's divide both size by $2^n * 2^n$, for fun and profit.
\[\frac{1}{2^n * 2^n}\abs{\sum_{a \in A, b \in B} (-1)^{M_{a,b}}} \geq 1 / K\]
We are mathematicians, and mathematicians like to name things.
Let's do that.
\begin{definition}[Discrepency]
The \emph{discrepency} of a rectangle $A \times B$ of $M(f)$ is exactly the following.
\[\emph{Disc}(A \times B) = \frac{1}{2^n * 2^n}\abs{\sum_{a \in A, b \in B} (-1)^{M_{a,b}}}\]
The \emph{discrency of $M(f)$} is the maximum discrepency among all its rectangles.
\end{definition}
Now that we've named this thing, let's re-write our inequality.
\[\emph{Disc}(A \times B) \geq 1 / K\]
Taking inverses:
\[\frac{1}{\emph{Disc}(A \times B)} \leq K\]
Certainly $\chi(f) \leq \chi(f)$, so supplanting $\chi(f)$ for $K$ in the statement, we get:
\begin{equation}
\frac{1}{\emph{Disc}(A \times B)} \leq \chi(f)
\label{eqRes}
\end{equation}
This result generalizes as follows.
\begin{lemma}[2-Party Discrepency Method]
Suppose $f : \mathbb{B}^n \times \mathbb{B}^n \to \mathbb{B}$ is a function.
Then Equation~\ref{eqRes} holds.
\end{lemma}
\end{document}